Blowship

### 2014-03-04 paper.tex
Penguinnn

\documentclass{paper}
\usepackage{authblk}

@@

Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut 
\section{Another Section} labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
\end{document}

>>>>

\documentclass{paper}
\usepackage{authblk}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage[margin=1.0in]{geometry}

@@

Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut
\section{Privacy Goals}
  The goal of this system is to provide an in-browser method for communicating securely between parties without massive latency or communication overhead. We attempt to satisfy these requirements assuming the intermediate server may be compromised. By communicating securely we mean specifically (using terminology from \textbf{[6]}):
  \\\\\textbf{Communication Privacy}. Any party Eve cannot read the contents of intercepted messages sent between any two parties Alice and Bob. 
  \\\textbf{Participant Privacy}. Any party Eve, cannot determine with probability $p > \epsilon$ that the two are communicating, given any $\epsilon$ chosen by Alice and Bob (with a clear lower bound of $\epsilon > 1/N$ where $N$ is the number of participants). The ability of multiple participants to collude and determine this with $p > \epsilon$ must be well defined.
  \\\textbf{Destination Privacy}. Any party Eve in the network cannot determine the final destination of any party Alice's messages. This is a less stringent requirement than Participant Privacy.
\section{PSP}
In this section we introduce
$P2(S2P2)^nP$, or PSP for short. PSP is an alternative to P2P protocols in which peers communicate with eachother through an alternating chain of peer-server and server-peer communications.
\\\\
\begin{figure}[ht]
  \includegraphics[width=290px]{PSP.png}
  \caption{A simple PSP communication chain}
\end{figure}
\\\\
\subsection{Adversaries}
In this context, we have several distinct types of adversaries we must consider:
\begin{enumerate}
  \item\textbf{Penguin.} Penguin is any Peer who can intercept and alter messages being passed through it. 
  \item\textbf{Surge.} Surge is a compromised central Server. He can alter and intercept any messages passing through, and can provide bogus information to any peer.
  \item\textbf{Proletariat.} The Proletariat is a group of colluding Penguins.
  \item\textbf{The Palace.} The Palace is a collusion of the Proletariat and Surge.
\end{enumerate}
\subsection{Basic Protocol}
Assume that Alice has obtained Bob's public key and unique ID while maintaining her anonymity. Assume also that Alice can obtain the public keys and IDs for $n \le N$ peers at random while hiding her choice from Surge.

Alice can then send a message to bob that will follow the path $A \rightarrow P_1 \rightarrow S \rightarrow ... \rightarrow S \rightarrow P_n \rightarrow B$ by sending the following message to Surge: 
\\\\
Let $M = E_{KRA}[  time || nonce || message ]$
\\Let $F_{ij}[x] = E_{KUi}[ ID_j || E_{KUj}[ x ] ]$
\\
Alice sends: $F_{S1}[F_{S2}[...F_{nB}[ M ]]]$ to Surge.

Each successive party receives a message and an ID to forward that message to, and only that party can read its message. Importantly, any non-colluding Penguin doesn't gain any information about the source or destination of the message it's passing along.

\subsection{Security Flaws}
Here we'll perform a simplified analysis of the security flaws of this system.
Let $P_{AB}$ be the probability that Alice is talking to Bob. 
\begin{enumerate}
\item\textbf{Linear Chain.} If we assume that Alice's message is the only message sent by any of $P_1 ... P_n$, $Surge$ can determine that $P_{AB} > 1/(n+1) \gg 1/N$. This is because Surge knows that one of $A \cup \{P_1 ... P_n\}$ talked to Bob.
\item\textbf{Collusion.} If there is a Proletariat of size $s$ colluding with Surge to form the Palace, then the Palace can determine on average (depending on which peers were picked), that $P_{AB} >1/(n/(N-s)+1)$ - that is, Alice has a chance $1 - (N-s)/N$ of each peer being compromised and not contributing to her privacy.
\item\textbf{Timing.} Even if $P_1 ... P_n$ are sending other messages, if Surge knows the probability distribution of the peer delay between receiving a message and forwarding it, he can discover the increased probability that Alice and Bob are talking. 
\item\textbf{Multiple Communications.} If Alice sends another message to Bob, or Bob back to Alice, the chance that they are communicating increases even more. 
\end{enumerate}
This is fairly poor security. If Alice chooses $n = 5$, then if her chosen peers send no other messages until hers is delivered, Surge knows $P_{AB} > 1/6$ chance that Alice is talking to Bob. If $60\%$ of peers are part of the Palace, then Surge possibly knows $P_{AB} = 1$ if $n \subset s$, but the expectation is $E[P_{AB}] = 1/3$.

\subsection{Solutions}
To begin solving these problems, change the protocol so that any non-Penguin peer will always send two or more messages simultaneously.

If we assume that there is not a Palace, then Alice needs only choose $n = log(N)$, and then Surge can only tell that $P_{AB} > 1 / 2^{log(N)} = 1/N $. In this way Surge gains no information about $P_{AB}$. If Surge knows Alice will choose $n = log(N)$, then he can rule out any peer in the chain with distance $< n$ from Alice, and then $P_{AB} > 1 / 2^{log(N) - 1} = 2/N$, which is still reasonable. 
\\\\
\textbf{The Palace.} Assuming there is a Palace $S$ with $s = |S| > n$ peers, and Alice chooses her $|R| = n$ peers randomly, there is unfortunately some chance that $R \subset S$ and so $P_{AB} = 1$. If $s = \phi*N$ peers are part of the palace, on average $E[P_{AB}] = 1 / 2^{\phi log(N)}$. The chance Surge can tell with probability $> \gamma$ that Alice and Bob are talking to eachother, $p(P_{AB} > \gamma)$ requires Alice choosing $x$ Palace members as peers.

\\This happens with probability $\sum\limits_{i=x}^n\phi^i$ where 
\\ $P_{AB} = 1 / 2^{n - x} = 1 / 2^{log(N) - x} = \gamma$
\\ $x = 2^{loglog(N)/\gamma}$

\begin{figure}[ht]
    \begin{tabular}{| l | l | l | l | l | l |}
      \hline
      $\phi$ & N & $E[P_{AB}]$ & x & n & $p(P_{AB} > 0.5)$ \\\hline
      0.5 & 1000 & 0.031 & 4 & 10 & 0.12\\
      0.5 & 10000 & 0.01 & 4 & 14 & 0.12\\
      0.5 & 100000 & 0.003 & 5 & 17 & 0.06\\
      \hline
    \end{tabular}
    \caption{Table 42.42 - Probabilities things are bad}
\end{figure}

While less than ideal this is not bad. The chance that Surge, having $50\%$ of peers colluding with him, can tell that Alice is talking to Bob with probability $> 0.5$ is only $12\%$. 
\\\\
\textbf{The Dictatorship.}
Unfortunately, if peers discover eachother through Surge, he can ensure that $\phi = 1$ by only sharing information about peers who are part of the Palace. 
\\\\
This is still a problem.
\end{document}
